% ShiTsuAmbiguity
\subsection{\jtl{shi} and \jtl{tsu} Ambiguity} \label{subsec:ShiTsuAmbiguity}

% シ
% ツ

The Katakana characters \jquotesingleja{シ} and \jquotesingleja{ツ} are
difficult to distinguish.  Both are made out of 3 strokes and even the length
are equal. In a sentence of course the context can help a lot. But what are the
rules for this characters to write properly and distinguish?

\bigskip

\begin{figure}[H]
\begin{center}
\begin{tabular}{|c|c|}\hline
\KLETTER{shi}&\KLETTER{tsu}\\\hline
\end{tabular}
\end{center}
\caption{\jtl{shi} and \jtl{tsu} ambiguity}
\label{fig:ShiAndTsuAmbiguity}
\end{figure}

\CharacterExplanation{shiexplanation}{

To write the letter \jtl{shi} it is important to align three lines
\textbf{vertically} (red line) and to \textbf{non-align} the ends (blue line).
In this way it is possible to distinguish \jtl{shi} from \jtl{tsu}. Of course
also the angle of the frist two lines are different, but in hadwriting this is
difficult to match. As a rule of thumb make the third line double as long as
the first two but short enough to not align it at the end.

}

\CharacterExplanation{tsuexplanation}{

To write the letter \jtl{tsu} it is important to align all tree lines
\textbf{horizontally} (red line) and to \textbf{non-align} the ends (blue
line). In this way it is possible to distinguish \jtl{tsu} from \jtl{shi}. Of
course also the angle of the first two lines are different, but in handwriting
this is difficult to match. As a rule of thumb make the third line double as
long as the first two but short enough to not align it at the end.

}

