% SoRiNAmbiguity
\subsection{\jtl{so}, \jtl{ri} and \jtl{n} Ambiguity} \label{subsec:SoRiNAmbiguity}

The Katakana characters \jquotesingleja{ソ}, \jquotesingleja{リ} and
\jquotesingleja{ン} can be difficult to distinguish. All three are made out of
only 2 strokes. And especially \jtl{so} and \jtl{n} can be hard to tell. In a
sentence of course the context can help a lot.  But what are the rules for this
characters to write properly and distinguish?

\bigskip

\begin{figure}[H]
\begin{center}
\begin{tabular}{|c|c|c|}\hline
\KLETTER{so}&\KLETTER{n}&\KLETTER{ri}\\\hline
\end{tabular}
\end{center}
\caption{\jtl{so}, \jtl{ri} and \jtl{n} ambiguity}
\label{fig:SoRiAndNAmbiguity}
\end{figure}

\CharacterExplanation{soexplanation}{

To write the letter \jtl{so} it is important to align both lines
\textbf{horizontally} (red line) and to \textbf{non-align} the ends (blue line)
vertically. In this way it is possible to distinguish \jtl{so} from \jtl{n},
but not from \jtl{ri}. To also distinguish it from \jtl{ri} you have to write
the first stroke not horizontally nor vertically (green line).

}

\CharacterExplanation{nexplanation}{

To write the letter \jtl{n} it is important to a align both lines
\textbf{vertically} (red line) and to \textbf{non-align} the ends (blue line).
In this way it is possible to distinguish \jtl{n} from \jtl{so}. If both lines
are aligned there should not be a problem to distinguish it from \jtl{ri}.
Usually the angle of the green line is different, but only a small indicator.

}

\CharacterExplanation{riexplanation}{

To write the letter \jtl{ri} it is important to \textbf{align} both of the line
beginnings \textbf{horizontally} (red line) and to make sure that both lines
are \textbf{parallel} (green lines). There should be \textbf{no alignment} on
the left side (blue line) \textbf{vertically}. The difference between \jtl{so}
and \jtl{ri} is that \jtl{ri} need to start with two \textbf{parallel} lines
wile \jtl{so} should not. Please compare the left green line for an
explanation.

}

