% ---------------------------------------------------------------------------
\section{Katakana /na/ Row}\jsec{片仮名ナ行}\label{sec:KatakanaNaRow}

\Krow{narow}{na}{ni}{nu}{ne}{no}

\label{letter:na}\KLETTER{na} The  片仮名 {「ナ」} is pronounced  /na/ and  derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Character}s {「奈」} upper left corner part.
A \hyperref[sec:Dakuten]{濁点} version  or \hyperref[sec:Handakuten]{半濁点} do
not exist.

\label{letter:ni}\KLETTER{ni} The  片仮名 {「ニ」} is pronounced  /ni/ and  derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Character}s {「奈」} upper right part.
A \hyperref[sec:Dakuten]{濁点} version  or \hyperref[sec:Handakuten]{半濁点} do
not exist.

\label{letter:nu}\KLETTER{nu} The  片仮名 {「ヌ」} is pronounced  /nu/ and  derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Character}s {「奴」} right part.
A \hyperref[sec:Dakuten]{濁点} version  or \hyperref[sec:Handakuten]{半濁点} do
not exist.

\input{../share/note/NuNoMeSimilarity}

\newpage

\label{letter:ne}\KLETTER{ne} The  片仮名 {「ネ」} is pronounced  /ne/ and  derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Character}s {「祢」} upper left  part.
A \hyperref[sec:Dakuten]{濁点} version  or \hyperref[sec:Handakuten]{半濁点} do
not exist.

\label{letter:no}\KLETTER{no} The  片仮名 {「ノ」} is pronounced  /no/ and  derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Character}s {「乃」} upper left part.
A \hyperref[sec:Dakuten]{濁点} version  or \hyperref[sec:Handakuten]{半濁点} do
not exist.

\input{../share/note/NuNoMeSimilarity}
\newpage

% ---------------------------------------------------------------------------
\subsection{/na/}\jsubsec{「ナ」} \label{sec:KatakanaNa}

\KatakanaHeader{na}{ Katakana /na/ is written with two strokes.} \KatakanaTraining{na}

% ---------------------------------------------------------------------------
\subsection{/ni/}\jsubsec{「ニ」} \label{sec:KatakanaNi}

\KatakanaHeader{ni}{ Katakana /ni/ is written with two strokes.} \KatakanaTraining{ni}

% ---------------------------------------------------------------------------
\subsection{/nu/}\jsubsec{「ヌ」} \label{sec:KatakanaNu}

\KatakanaHeader{nu}{Katakana /nu/ is written with two strokes.} \KatakanaTraining{nu}

% ---------------------------------------------------------------------------
\subsection{/ne/}\jsubsec{「ネ」} \label{sec:KatakanaNe}

\KatakanaHeader{ne}{Katakana /ne/ is written with three strokes.} \KatakanaTraining{ne}

% ---------------------------------------------------------------------------
\subsection{/no/}\jsubsec{「ノ」} \label{sec:KatakanaNo}

\KatakanaHeader{no}{Katakana /no/ is written with one stroke.} \KatakanaTraining{no}

% ---------------------------------------------------------------------------
\subsection{片仮名ナ行練習}\jsubsec{ /na/ Row Training}
\Padding
\begin{longtable}[c]{p{2cm}p{2cm}p{3cm}p{6cm}p{2cm}}
\textit{Katakana}&\textit{Rōmaji}&\textit{Original}&\textit{Remark}&\textit{Origin}\\\hline
ナース  &nāsu &nurse      &                                        &English\\
ネット  &netto&net(work)  &                                        &English\\
アニス　&anisu&anise      &pimpinella anisum                       &\\
\end{longtable}

\KatakanaSimpleTraining{Katakana to Rōmaji}{
\Transcribe{1.}{ネット}{}{net(work)}
\Transcribe{2.}{ナース}{}{nurse}
\Transcribe{3.}{アニス}{}{anise}
\Transcribe{4.}{ニート}{}{NEET}
\Transcribe{5.}{ナイター}{}{night + -er}
%\Transcribe{6.}{ノート}{}{note}
}

\KatakanaSimpleTraining{Rōmaji to Katakana}{
\Transcribe{1.}{nōto}{}{note}
\Transcribe{2.}{netto}{}{net(work)}
\Transcribe{3.}{anisu}{}{anise}
\Transcribe{4.}{nāsu}{}{nurse}
\Transcribe{5.}{naitā}{}{night + -er}
%\Transcribe{4.}{ニート}{}{NEET}
}

\newpage
\Padding
\begin{longtable}[c]{p{2cm}p{2cm}p{3cm}p{6cm}p{2cm}}
\textit{Katakana}&\textit{Rōmaji}&\textit{Original}&\textit{Remark}&\textit{Origin}\\\hline
ニート  &nīto &NEET       &Not in Education, Employment or Training&English\\
ナイター&naitā&night + -er&     a night game                       &English\\
ノート  &nōto &note       & note, notebook                         &English\\
\end{longtable}
\KatakanaSimpleTraining{English to Rōmaji}{
\Transcribe{1.}{anise}{}{}
\Transcribe{2.}{net(work)}{}{}
\Transcribe{3.}{note}{}{}
\Transcribe{4.}{nurse}{}{}
\Transcribe{5.}{NEET}{}{}
%\Transcribe{5.}{night + -er}{}{}
}

\KatakanaSimpleTraining{English to Katakana}{
\Transcribe{1.}{nurse}{}{}
\Transcribe{2.}{note}{}{}
\Transcribe{3.}{net(work)}{}{}
\Transcribe{4.}{anise}{}{}
\Transcribe{5.}{night + -er}{}{}
%\Transcribe{4.}{NEET}{}{}
}

\newpage
