%----------------------------------------------------------------------------
\section{Katakana /a/ Row}\jsec{ 片仮名ア行}\label{sec:KatakanaARow}

\Krow{arow}{a}{i}{u}{e}{o}

\label{letter:a}\KLETTER{a} The 片仮名 {「ア」} derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Characters}
(\hyperref[sec:Radical]{radical}).  A smaller version {「ァ」} is used in
combinations with other letters as {「ファ」} and is pronounced as /fa/ in
\hyperref[sec:Hepburn]{Hepburn} transcription.

\label{letter:u}\KLETTER{i} The 片仮名 {「イ」} derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Characters} {「伊」} left element
(\hyperref[sec:Radical]{radical}).  A smaller version {「ィ」} is used in
combinations with other letters and represents a
\hyperref[sec:Diphthong]{diphthong}. 

\label{letter:u}\KLETTER{u} The 片仮名 {「ウ」} derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Character} {「宇」}. A smaller version
{「ゥ」} is used in combinations with other letters and represents a
\hyperref[sec:Diphthong]{diphthong} and is written as "w". Even though the
combination {「トゥ」} /tu/ exist, it is relatively new and many words do not
use it. In this cases {「ツ 」} /tsu/ is used. {「ウ」} can take
\hyperref[sec:Dakuten]{Dakuten} to form {「ヴ」} /vu/, which is relatively new
and can replace {「ブ」} /bu/. 

\input{../share/note/UFuWaSimilarity}

\newpage 

\label{letter:e}\KLETTER{e} The 片仮名 {「エ」} derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Characters} {「江」} right element
(\hyperref[sec:Radical]{radical}). A smaller version {「ェ」} is used in
combinations with other letters and express \hyperref[sec:Mora]{morae} of
foreign origin. For example {「ヴェ」} as pronounced /ve/.

\label{letter:o}\KLETTER{o} The 片仮名 {「オ」} derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Character} {「於」}. A smaller version
{「ォ」} is used in combinations with other letters and express
\hyperref[sec:Mora]{morae} of foreign origin. For example {「フォ 」} as
pronounced /fe/.

\newpage

% ---------------------------------------------------------------------------
\subsection{/a/}\jsubsec{「ア」} \label{sec:KatakanaA}

\KatakanaHeader{a}{ The Katakana {「ア」} is written with two strokes. The
first stroke starts horizontal. The second stroke is a curve with can be
attached to the first stroke in hand writing, but not at the horizontal part -
at the end of the first line.} \KatakanaTraining{a}

% ---------------------------------------------------------------------------
\subsection{/i/}\jsubsec{「イ」} \label{sec:KatakanaI}

\KatakanaHeader{i}{ The Katakana {「イ」} is written with one stroke. The first
stroke is a curve from upper right to lower left. The second stroke is a
vertical line attached to the first at the top.} \KatakanaTraining{i}

% ---------------------------------------------------------------------------
\subsection{/u/}\jsubsec{「ウ」} \label{sec:KatakanaU}

\KatakanaHeader{u}{The Katakana {「ウ」} is written with three strokes. The
first stroke a small vertical line. The second a small vertical line again and
the third line a horizontal line connection the two others.}
\KatakanaTraining{u}

% ---------------------------------------------------------------------------
\subsection{/e/}\jsubsec{「エ」} \label{sec:KatakanaE}

\KatakanaHeader{e}{The Katakana {「エ」} is written with three strokes. It is
very geometrically consisting only out of horizontal and vertical lines
connected together.} \KatakanaTraining{e}

% ---------------------------------------------------------------------------
\subsection{/o/}\jsubsec{「オ」} \label{sec:KatakanaO}

\KatakanaHeader{o}{The Katakana {「オ」} is written with three strokes. The
first line is horizontal and together with the second stroke it constructs a
perfect crossing. The third stroke beginning lies at the center of the
crossing.} \KatakanaTraining{o}

% ---------------------------------------------------------------------------
\subsection{/a/ Row Training}\jsubsec{片仮名ア行練習}
\Padding
\begin{longtable}[c]{p{2cm}p{2cm}p{3cm}p{6cm}p{2cm}}
\textit{Katakana}&\textit{Rōmaji}&\textit{Original}&\textit{Remark}&Origin\\\hline
ウエア&wuea&ware&          &English\\
エア  &ea  &air &          &English\\
エイ  &ei  &A   &the letter&English\\
\end{longtable}

\KatakanaSimpleTraining{Katakana to Rōmaji}{
\Transcribe{1.}{ウエア}{}{wear, ware}
\Transcribe{2.}{エア}{}{air}
\Transcribe{3.}{エイ}{}{A (the letter)}
\Transcribe{4.}{アイ}{}{I (the letter)}
\Transcribe{5.}{オウ}{}{O (the letter)}
%\Transcribe{6.}{イア}{}{ear}
}

\KatakanaSimpleTraining{Rōmaji to Katakana}{
\Transcribe{1.}{ea}{}{air}
\Transcribe{2.}{ai}{}{I (the letter)}
\Transcribe{3.}{ou}{}{O (the letter)}
\Transcribe{4.}{ei}{}{A (the letter)}
\Transcribe{5.}{uea}{}{wear, ware}
%\Transcribe{6.}{ia}{}{ear}
}

\newpage
\Padding
\begin{longtable}[c]{p{2cm}p{2cm}p{3cm}p{6cm}p{2cm}}
\textit{Katakana}&\textit{Rōmaji}&\textit{Original}&\textit{Remark}&Origin\\\hline
アイ  &ai  &I   &the letter&English\\
オウ  &ou  &O   &the letter&English\\
イア  &ia  &ear &          &English\\
\end{longtable}

\KatakanaSimpleTraining{English to Rōmaji}{
\Transcribe{1.}{ear}{}{}
\Transcribe{2.}{I (the letter)}{}{}
\Transcribe{3.}{air}{}{}
\Transcribe{4.}{O (the letter)}{}{}
\Transcribe{5.}{wear, ware}{}{}
%\Transcribe{6.}{A (the letter)}{}{}
}

\KatakanaSimpleTraining{English to Katakana}{
\Transcribe{1.}{I (the letter)}{}{}
\Transcribe{2.}{O (the letter)}{}{}
\Transcribe{3.}{air}{}{}
\Transcribe{4.}{ear}{}{}
\Transcribe{5.}{wear, ware}{}{}
%\Transcribe{6.}{A (the letter)}{}{}
}
\newpage
