% ---------------------------------------------------------------------------
\section{Katakana /ma/ Row - 片仮名マ行}\label{sec:KatakanaMaRow}

\Krow{marow}{ma}{mi}{mu}{me}{mo}

\label{letter:ma}\KLETTER{ma} The  片仮名 {「マ」} is pronounced  /ma/ and
derives from the \hyperref[sec:PhoneticCharacter]{Phonetic Character}s {「末」}
upper two parallel horizontal strokes.  A \hyperref[sec:Dakuten]{濁点} or
\hyperref[sec:Handakuten]{半濁点} version do not exist.

\label{letter:mi}\KLETTER{mi} The  片仮名 {「ミ」} is pronounced  /mi/ and
derives from the \hyperref[sec:PhoneticCharacter]{Phonetic Character} {「三」}.
A \hyperref[sec:Dakuten]{濁点} or \hyperref[sec:Handakuten]{半濁点} version do
not exist.

\label{letter:mu}\KLETTER{mu} The  片仮名 {「ム」} is pronounced  /mu/ and
derives from the \hyperref[sec:PhoneticCharacter]{Phonetic Character}s {「牟
」} upper part.  A \hyperref[sec:Dakuten]{濁点} or
\hyperref[sec:Handakuten]{半濁点} version do not exist.

\newpage

\label{letter:me}\KLETTER{me} The  片仮名 {「メ」} is pronounced  /me/ and
derives from the \hyperref[sec:PhoneticCharacter]{Phonetic Character}s {「女」}
ilower right part.  A \hyperref[sec:Dakuten]{濁点} or
\hyperref[sec:Handakuten]{半濁点} version do not exist.

\input{../share/note/NuNoMeSimilarity}

\label{letter:mo}\KLETTER{mo} The  片仮名 {「モ」} is pronounced  /mo/ and
derives from the \hyperref[sec:PhoneticCharacter]{Phonetic Character}s {「毛」}
ilower part exluding the first stroke.  A \hyperref[sec:Dakuten]{濁点} or
\hyperref[sec:Handakuten]{半濁点} version do not exist.

\newpage

\subsection{/ma/ - 「マ」} \label{sec:KatakanaMa}

\KatakanaHeader{ma}{ Katakana /ma/ is written with three strokes.}
\KatakanaTraining{ma}

\subsection{/mi/ - 「ミ」} \label{sec:KatakanaMi}

\KatakanaHeader{mi}{ Katakana /mi/ is written with three strokes.}
\KatakanaTraining{mi}

\subsection{/mu/ - 「ム」} \label{sec:KatakanaMu}

\KatakanaHeader{mu}{ Katakana /mu/ is written with three strokes.}
\KatakanaTraining{mu}

\subsection{/me/ - 「メ」/} \label{sec:KatakanaMe}

\KatakanaHeader{me}{ Katakana /me/ is written with three strokes.}
\KatakanaTraining{me}

\subsection{/mo/ - 「モ」} \label{sec:KatakanaMo}

\KatakanaHeader{mo}{ Katakana /mo/ is written with three strokes.}
\KatakanaTraining{mo}

\subsection{/ma/ Row Training - 片仮名マ行練習}
\Padding
\begin{longtable}[c]{p{2cm}p{1.5cm}p{2.5cm}p{3cm}p{5cm}}
\textit{Katakana}&\textit{Rōmaji}&\textit{Original}&\textit{Remark}&Origin\\\hline
テーマ  &tēma    &Thema                 &theme                 &German\\
ママ    &mama    &mamá                  &mom                   &Spanish\\
ホーム  &hōmu    &(plat)form            &railway platform      &English\\
\end{longtable}

%シーエム        shīemu    C.M. (Commercial Message)       television commercial   English
%アニメ          anime     anima(tion)                  animated cartoons or films English

\KatakanaSimpleTraining{Katakana to Rōmaji}{
\Transcribe{1.}{テーマ}{}{theme}
\Transcribe{2.}{ママ}{}{mom}
\Transcribe{3.}{ホーム}{}{railway platform }
\Transcribe{4.}{アメフト}{}{American football}
\Transcribe{5.}{ハモる}{}{to harmonize (singing)}
%\Transcribe{6.}{マスコミ}{}{mass media}
}

\KatakanaSimpleTraining{Rōmaji to Katakana}{
\Transcribe{1.}{mama}{}{mom}
\Transcribe{2.}{tēma}{}{theme}
\Transcribe{3.}{amefuto}{}{American football}
\Transcribe{4.}{masukomi}{}{mass media}
\Transcribe{5.}{hōmu}{}{railway platform }
%\Transcribe{6.}{hamoru}{}{to harmonize (singing)}
}

\newpage
\Padding
\begin{longtable}[c]{p{2cm}p{2cm}p{4cm}p{4cm}p{3cm}}
\textit{Katakana}&\textit{Rōmaji}&\textit{Original}&\textit{Remark}&Origin\\\hline
アメフト&amefuto &Ame(rican) foot(ball) &American football     &English\\
ハモる  &hamoru  &harmo(ny) + -ru       &to harmonize (singing)&English, Japanese\\
マスコミ&masukomi&mass communication    &mass media            &English\\
\end{longtable}
\KatakanaSimpleTraining{English to Rōmaji}{
\Transcribe{1.}{theme}{}{}
\Transcribe{2.}{American football}{}{}
\Transcribe{2.}{mom}{}{}
\Transcribe{3.}{to harmonize (singing)}{}{}
\Transcribe{4.}{railway platform }{}{}
%\Transcribe{5.}{mass media}{}{}
}

\KatakanaSimpleTraining{English to Katakana}{
\Transcribe{1.}{American football}{}{}
\Transcribe{2.}{mom}{}{}
\Transcribe{3.}{railway platform }{}{}
\Transcribe{4.}{theme}{}{}
\Transcribe{5.}{mass media}{}{}
%\Transcribe{6.}{to harmonize (singing)}{}{}
}

\newpage
