% ---------------------------------------------------------------------------
\section{Katakana /ra/ row - 片仮名ラ行}\label{sec:KatakanaRaRow}

\Krow{rarow}{ra}{ri}{ru}{re}{ro}

\KLETTER{ra} The  片仮名 {「ラ」} is pronounced  /ra/ (flapped 'r')  and  derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Character}s {「良」} upper right corner part.
A \hyperref[sec:Dakuten]{濁点}  or \hyperref[sec:Handakuten]{半濁点} version  do not exist.

\Note{Note}{
\input{../share/para/FlappedPronunciation}
}

\KLETTER{ri} The  片仮名 {「リ」} is pronounced  /ri/ (flapped 'r')  and  derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Character}s {「利」}  right site part.
A \hyperref[sec:Dakuten]{濁点}  or \hyperref[sec:Handakuten]{半濁点} version  do not exist.

%\Note{Note}{Please see section \nameref{subsec:SoRiNAmbiguity} for the explanation
%how to write and distinguish /so/, /n/ and /ri/.
%}


\KLETTER{ru} The  片仮名 {「ル」} is pronounced  /ru/ (flapped 'r')  and  derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Character}s {「流」} lower left corner part.
A \hyperref[sec:Dakuten]{濁点}  or \hyperref[sec:Handakuten]{半濁点} version  do not exist.


\KLETTER{re} The  片仮名 {「レ」} is pronounced  /re/ (flapped 'r')  and  derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Character}s {「礼」} upper right site part.
A \hyperref[sec:Dakuten]{濁点}  or \hyperref[sec:Handakuten]{半濁点} version  do not exist.

\KLETTER{ro} The  片仮名 {「ロ」} is pronounced  /ro/ (flapped 'r')  and  derives from the
\hyperref[sec:PhoneticCharacter]{Phonetic Character}s {「呂」} upper part.
A \hyperref[sec:Dakuten]{濁点}  or \hyperref[sec:Handakuten]{半濁点} version  do not exist.

\input{../share/subsec/SoRiNAmbiguity}

\newpage

% ラリルレロ
\subsection{/ra/ - 「ラ」} \label{sec:KatakanaRa}

\KatakanaHeader{ra}{ Katakana /ra/ is written with two strokes.} \KatakanaTraining{ra}

\subsection{/ri/ - 「リ」} \label{sec:KatakanaRi}

\KatakanaHeader{ri}{ Katakana /ri/ is written with two strokes.} \KatakanaTraining{ri}

\subsection{/ru/ - 「ル」} \label{sec:KatakanaRu}

\KatakanaHeader{ru}{ Katakana /ru/ is written with two strokes.} \KatakanaTraining{ru}

\subsection{/re/ - 「レ」} \label{sec:KatakanaRe}

\KatakanaHeader{re}{ Katakana /re/ is written with one stroke.} \KatakanaTraining{re}

\subsection{/ro/ - 「ロ」} \label{sec:KatakanaRa}

\KatakanaHeader{ro}{ Katakana /ro/ is written with three strokes.} \KatakanaTraining{ro}

\subsection{/ra/ Row Training - 片仮名ラ行練習}
\Padding
\begin{longtable}[c]{p{2cm}p{1.5cm}p{2.5cm}p{3cm}p{6cm}}
\textit{Katakana}&\textit{Rōmaji}&\textit{Original}&\textit{Remark}&Origin\\\hline
ヒステリー  &hisuterī  &Hysterie      &hysteria               &German\\
メール      &mēru      &e-mail        &electronic mail        &English\\
イラスト    &irasuto   &illust(ration)&illustration           &English\\
\end{longtable}
\Padding

%ロスタイム      rosutaimu       loss time       added time, additional time     English


\KatakanaSimpleTraining{Katakana to Rōmaji}{
\Transcribe{1.}{ヒステリー}{}{hysteria}
\Transcribe{2.}{メール}{}{e-mail}
\Transcribe{3.}{イラスト}{}{illustration}
\Transcribe{4.}{プレイガイド}{}{play guide}
\Transcribe{5.}{ノイローゼ}{}{neurosis}
\Transcribe{6.}{アロエ}{}{aloe}
}

\KatakanaSimpleTraining{Rōmaji to Katakana}{
\Transcribe{1.}{mēru}{}{e-mail}
%\Transcribe{2.}{irasuto}{}{illustration}
\Transcribe{3.}{hisuterī}{}{hysteria}
\Transcribe{4.}{noirōze}{}{neurosis}
\Transcribe{5.}{pureigaido}{}{play guide}
\Transcribe{6.}{aroe}{}{aloe}
}

\newpage
\begin{longtable}[c]{p{2.5cm}p{2.5cm}p{2.5cm}p{5.5cm}p{2cm}}
\textit{Katakana}&\textit{Rōmaji}&\textit{Original}&\textit{Remark}&Origin\\\hline
プレイガイド&pureigaido&play + guide  &(theater) ticket agency&English\\
ノイローゼ  &noirōze   &Neurose       &neurosis               &German\\
アロエ      &aroe      &Aloë          &aloe                   &Dutch\\
\end{longtable}
\KatakanaSimpleTraining{English to Rōmaji}{
%\Transcribe{1.}{e-mail}{}{}
\Transcribe{2.}{play guide}{}{}
\Transcribe{3.}{hysteria}{}{}
\Transcribe{4.}{neurosis}{}{}
\Transcribe{5.}{illustration}{}{}
\Transcribe{6.}{aloe}{}{}
}

\KatakanaSimpleTraining{English to Katakana}{
\Transcribe{1.}{illustration}{}{}
%\Transcribe{2.}{play guide}{}{}
\Transcribe{3.}{aloe}{}{}
\Transcribe{4.}{neurosis}{}{}
\Transcribe{5.}{hysteria}{}{}
\Transcribe{6.}{mēru}{}{e-mail}
}

\newpage
