% ---------------------------------------------------------------------------
\section{部首- Radical} \label{sec:Radical}

A radical {部首} {【ぶしゅ】} is a root particle or character of a Sino-Japanese 
character {漢字} {【かんじ】}. It is the most significant part of a Sino-Japanese
character. The concept was developed in China for Chinese characters and is
today known under the same name {部首} (pinyin: bùshǒu).

There is no general definition what a radical is or how many are existing and it 
can vary a lot. The author of a dictionary has the power to defined what a radical
is and how much there will be in that dictionary.

In more traditional Chinese or Japanese dictionaries a number of 214 or 244
radicals is quite common. However some modern approaches like the
\href{http://www.hadamitzky.de/english/works_books.htm#KD}{\textit{The Kanji
Dictionary} of Marc Spahn and Wolfgang Hadamitzky from 1996} a totally
different number of 79 can be found.

\Note{Note}{\footnotesize Before buying a {漢字} dictionary, make sure that the
radical system used suits your taste. Sometimes it can be observed that
Japanese dictionaries are stricter in the definition of a radical because a
given {漢字} can only be retrieved via exactly \textbf{one} radical. While in
many Chinese dictionaries \textbf{every} radical of a Chinese character can be
used to find it. The Japanese approach is of course good in terms of systematic
and didactic for learners, however it can take significant longer to look up a
character by radical.  }

