\documentclass[paper=a4,headings=small,titlepage,makeidx,fontsize=12pt]{scrbook} 

% ===========================================================================
% PREAMBLE
% ===========================================================================
\input{../share/preamble/standard-english}

% SIMPLE COMMANDS
\input{../share/cmd/AutorName}
\input{../share/cmd/NumberTwo}
\input{../share/cmd/TitlePicture}
\input{../share/cmd/Kletter}
\input{../share/cmd/KLETTER}
\input{../share/cmd/Link}

% PARAGRAPH COMMANDS
\input{../share/box/Warn} % red   - additional dangerous info reg. lang
\input{../share/box/Hint} % blue  - additional important info reg. lang
\input{../share/box/Info} % green - additional important info
\input{../share/box/Note} % gray  - additional info
\input{../share/cmd/Krow} % 6 parameters
\input{../share/cmd/Transcibe}

% PAGE COMMANDS
\input{../share/katakana/training.tex}
\input{../share/katakana/header.tex}

% TITLE
\input{title}

% ===========================================================================
% DOCUMENT
% ===========================================================================
\begin{document}
\pagestyle{plain}
\frontmatter
\maketitle

% CONTENTS
\tableofcontents
\pagestyle{fancy}

\mainmatter

% ===========================================================================
\chapter{片仮名 - Katakana}

\Warn{Warning!}{This work is a \textbf{draft}. It is not complete and contains errors.  Please report.}

\bigskip

Katakana, written as {片仮名 【かたかな】} or {カタカナ} is the second Japanese
\hyperref[sec:Syllable]{syllable} writing system. 



% ---------------------------------------------------------------------------
\chapter{片仮名練習 - Katakana Training}

todo
\newpage
\section{片仮名 ア行 - Katakana |a| row}

\Krow{arow}{a}{i}{u}{e}{o}

\KLETTER{a}
The 片仮名 {「ア」} derives from the
\hyperref[sec:Manyogana]{万葉仮名} characters {「阿」} left element
(\hyperref[sec:Radical]{radical}).  A smaller version {「ァ」} is used in
combinations with other letters as {「ファ」} and is pronounced as |fa| in
\hyperref[sec:Hepburn]{Hepburn} transcription.

\KLETTER{i}
The 片仮名 {「イ」} derives from the
\hyperref[sec:Manyogana]{万葉仮名} characters {「伊」} left element
(\hyperref[sec:Radical]{radical}).  A smaller version {「ィ」} is used in
combinations with other letters and represents a
\hyperref[sec:Diphthong]{diphthong}. 

\KLETTER{u}
The 片仮名 {「ウ」} derives from the
\hyperref[sec:Manyogana]{万葉仮名} character {「宇」}. A smaller version
{「ゥ」} is used in combinations with other letters and represents a
\hyperref[sec:Diphthong]{diphthong} and is written as "w". Even though the
combination {「トゥ」} |tu| exist, it is relatively new and many words do not
use it. In this cases {「ツ 」} |tsu| is used. {「ウ」} can take
\hyperref[sec:Dakuten]{Dakuten} to form {「ヴ」} |vu|, which is relatively new
and can replace {「ブ」} |bu|. 

\KLETTER{e}
The 片仮名 {「エ」} derives from the
\hyperref[sec:Manyogana]{万葉仮名} characters {「江」} right element
(\hyperref[sec:Radical]{radical}). A smaller version {「ェ」} is used in
combinations with other letters and express \hyperref[sec:Mora]{morae} of
foreign origin. For example {「ヴェ」} as pronounced |ve|.

\KLETTER{o}
The 片仮名 {「オ」} derives from the
\hyperref[sec:Manyogana]{万葉仮名} character {「於」}. A smaller version
{「ォ」} is used in combinations with other letters and express
\hyperref[sec:Mora]{morae} of foreign origin. For example {「フォ 」} as
pronounced |fe|.

\newpage
TODO
\newpage


% ---------------------------------------------------------------------------
\subsection{片仮名:ア - |a|} \label{sec:KatakanaA}

\KatakanaHeader{a}{ TODO }

\KatakanaTraining{a}

% ---------------------------------------------------------------------------
\subsection{片仮名:イ - |i|} \label{sec:KatakanaI}

\KatakanaHeader{i}{ TODO } \KatakanaTraining{i}

% ---------------------------------------------------------------------------
\subsection{片仮名:ウ - |u|} \label{sec:KatakanaU}

\KatakanaHeader{u}{TODO } \KatakanaTraining{u}

% ---------------------------------------------------------------------------
\subsection{片仮名:エ - |e|} \label{sec:KatakanaE}

\KatakanaHeader{e}{ TODO } \KatakanaTraining{e}

% ---------------------------------------------------------------------------
\subsection{片仮名:オ - |o|} \label{sec:KatakanaO}

\KatakanaHeader{o}{TODO} \KatakanaTraining{o}

\section{片仮名ア行練習 -  a-row Training}

\subsection{Training 1 Katakana $\Longrightarrow$ Romaji}

Please transcribe the following words from Katakana to Romaji:

\fbox{
\begin{minipage}{17cm}
\bigskip
\begin{center}
\Transcribe{1.}{ウエア}{}{wear, ware}
\Transcribe{2.}{エア}{}{air}
\Transcribe{3.}{エイ}{}{A (the letter)}
\Transcribe{4.}{アイ}{}{I (the letter)}
\Transcribe{5.}{オウ}{}{O (the letter)}
\Transcribe{6.}{イア}{}{ear}
\bigskip
\end{center}
\end{minipage}
}

\subsection{Training 2 Romaji $\Longrightarrow$ Katakana}

Please transcribe the following words from Romaji to Katakana:

\fbox{
\begin{minipage}{17cm}
\bigskip
\begin{center}
\Transcribe{1.}{ea}{}{air}
\Transcribe{2.}{ai}{}{I (the letter)}
\Transcribe{3.}{ou}{}{O (the letter)}
\Transcribe{4.}{ei}{}{A (the letter)}
\Transcribe{5.}{uea}{}{wear, ware}
\Transcribe{6.}{ia}{}{ear}
\bigskip
\end{center}
\end{minipage}
}

\newpage

\subsection{Training 3 English $\Longrightarrow$ Romaji}

Please transcribe the following words from English to Romaji:

\fbox{
\begin{minipage}{17cm}
\bigskip
\begin{center}
\Transcribe{1.}{ear}{}{}
\Transcribe{2.}{I (the letter)}{}{}
\Transcribe{3.}{air}{}{}
\Transcribe{4.}{O (the letter)}{}{}
\Transcribe{5.}{wear, ware}{}{}
\Transcribe{6.}{A (the letter)}{}{}
\bigskip
\end{center}
\end{minipage}
}

\subsection{Training 4 English $\Longrightarrow$ Katakana}

Please transcribe the following words from English to Katakana:

\fbox{
\begin{minipage}{17cm}
\bigskip
\begin{center}
\Transcribe{2.}{I (the letter)}{}{}
\Transcribe{3.}{O (the letter)}{}{}
\Transcribe{1.}{air}{}{}
\Transcribe{6.}{ear}{}{}
\Transcribe{5.}{wear, ware}{}{}
\Transcribe{4.}{A (the letter)}{}{}
\bigskip
\end{center}
\end{minipage}
}
\newpage

\section{片仮名 カ行 - Katakana |ka| row}

\Krow{krow}{ka}{ki}{ku}{ke}{ko}

\KLETTER{ka} The  片仮名 {「カ」} is pronounced  |ka| and  derives from the
\hyperref[sec:Manyogana]{万葉仮名} characters {「加」} left
\hyperref[sec:Radical]{radical}.  A \hyperref[sec:Dakuten]{濁点} version exists
and pronounced as |ga|.

%\hyperref[sec:Handakuten]{半濁点} does not exist in daily Japanese.  
% {「一ヵ所」} {【いちかしょ】} (one place)
% {「一ヶ所」} {【いちかしょ】} (one place).
% 十ヵ条（十ヶ条）


\Note{Note}{A smaller version {「ヵ」} is rare but used in combinations with number
particles.  For example in {「一ヵ月」} {【いっかげつ】} (one month) and
others.  This cases can also be written {「一ヶ月」} {【いっかげつ】} (one
month). Please see also \nameref{sec:KatakanaKe}. \Link
\href{http://ja.wikipedia.org/wiki/\%E3\%83\%B5}{ヵ} }

\KLETTER{ki} The 片仮名 {「キ」} derives from the
\hyperref[sec:Manyogana]{万葉仮名} characters middle part of either {「機」} or
{「幾」}.  It is pronounced as |ki|.  A \hyperref[sec:Dakuten]{濁点} version
exists and pronounced as |gi|.


\KLETTER{ku} The 片仮名 {「ク」} derives from the
\hyperref[sec:Manyogana]{万葉仮名} characters left upper part of {「久」}.  It
is pronounced as |ku|.  A \hyperref[sec:Dakuten]{濁点} version exists and
pronounced as |gu|.  A smaller version exists, but is used for the Ainu
Language.



\KLETTER{ke} The 片仮名 {「ケ」} derives from the
\hyperref[sec:Manyogana]{万葉仮名} characters upper and left part of {「介」}.
It is pronounced as |ke|.  A \hyperref[sec:Dakuten]{濁点} version exists and
pronounced as |ge|.  The smaller version {「ヶ」} is explained in the following note.

\newpage

\Note{Note}{ A smaller version {「ヶ」} is rare but used in combinations with
number particles.  For example in {「一ヶ月」} {【いっかげつ】} (one month) and
others.  This cases can also be written {「一ヵ月」} {【いっかげつ】} (one
month). There are cases where only {「ヶ」} can be written {七ヶ宿}
{【シチカシュク】} (Place at the south west border of the prefecture Miyagi).
In other rare cases this character can be pronounced different {「関ヶ原」}
{【せきがはら】}　(Place at the south border of the Gifu prefecture, known by
the battle at 1600.). Please see also \nameref{sec:KatakanaKa}. \Link
\href{http://ja.wikipedia.org/wiki/\%E3\%83\%B5}{ヵ} }

\KLETTER{ko} The 片仮名 {「コ」} derives from the
\hyperref[sec:Manyogana]{万葉仮名} characters upper part of {「己」}.  It is
pronounced as |ko|.  A \hyperref[sec:Dakuten]{濁点} version exists and
pronounced as |go|.



\newpage

\subsection{片仮名:カ - |ka|} \label{sec:KatakanaKa}

\KatakanaHeader{ka}{ |ka| is written with 2 strokes. Basically the same way as
the Hiragana {「か」} it looks like a squarish version, but without the last
stroke. The hook at the second stroke is less significant or important.  }
\KatakanaTraining{ka}

\subsection{片仮名:キ - |ki|} \label{sec:KatakanaKi}

\KatakanaHeader{ki}{ The shape alignment of the 「キ」character is not straight
towards its environment. However the junctions are more or less 90 degrees.  }
\KatakanaTraining{ki}

\subsection{片仮名:ク - |ku|} \label{sec:KatakanaKu}

\KatakanaHeader{ku}{ The first stroke is similar the stroke of {「ケ 」} is a
curve. While the second stroke start aligned and straight. }
\KatakanaTraining{ku}

\subsection{片仮名:ケ - |ke|} \label{sec:KatakanaKe}

\KatakanaHeader{ke}{ The {「ケ 」} is written with 3 strokes and the first
stroke is similar to the {「ク」}. The second stroke is aligned and straight.
While the last stroke is a curve.  } \KatakanaTraining{ke}

\subsection{片仮名:コ - |ko|} \label{sec:KatakanaKo}

\KatakanaHeader{ko}{ This character is almost a geometric figure composed out
of two strokes. However unless in European languages this are only 2 strokes
and not 3. The first stroke is the longest one and done similar with all
{漢字}. } \KatakanaTraining{ko}

\section{片仮名カ行練習 -  k-row Training}

\subsection{Training 1 Katakana $\Longrightarrow$ Romaji}

Please transcribe the following words from Katakana to Romaji:

\fbox{
\begin{minipage}{17cm}
\bigskip
\begin{center}
\Transcribe{1.}{カキ}{}{persimmon}
\Transcribe{2.}{ココア}{}{cocoa}
\Transcribe{3.}{ケア}{}{care}
\Transcribe{4.}{コア}{}{core}
\Transcribe{5.}{ケイ}{}{K (the letter)}
\Transcribe{6.}{ケーキ}{}{cake}
\bigskip
\end{center}
\end{minipage}
}

\subsection{Training 2 Romaji $\Longrightarrow$ Katakana}
Please transcribe the following words from Romaji to Katakana:

\fbox{
\begin{minipage}{17cm}
\bigskip
\begin{center}
\Transcribe{1.}{kokoa}{}{cocoa}
\Transcribe{2.}{k$\overline{\mbox{e}}$ki}{}{cake}
\Transcribe{3.}{kea}{}{care}
\Transcribe{4.}{koa}{}{core}
\Transcribe{5.}{kaki}{}{persimmon}
\Transcribe{6.}{kei}{}{K (the letter)}
\bigskip
\end{center}
\end{minipage}
}

\newpage
\subsection{Training 3 English $\Longrightarrow$ Romaji}

Please transcribe the following words from English to Romaji:

\fbox{
\begin{minipage}{17cm}
\bigskip
\begin{center}
\Transcribe{1.}{persimon}{}{}
\Transcribe{2.}{cocoa}{}{}
\Transcribe{3.}{care}{}{}
\Transcribe{4.}{core}{}{}
\Transcribe{5.}{K (the letter)}{}{}
\Transcribe{6.}{cake}{}{}
\bigskip
\end{center}
\end{minipage}
}

\subsection{Training 4 English $\Longrightarrow$ Katakana}

Please transcribe the following words from English to Katakana:

\fbox{
\begin{minipage}{17cm}
\bigskip
\begin{center}
\Transcribe{1.}{cocoa}{}{}
\Transcribe{2.}{cake}{}{}
\Transcribe{3.}{care}{}{}
\Transcribe{4.}{persimon}{}{}
\Transcribe{5.}{K (the letter)}{}{}
\Transcribe{6.}{core}{}{}
\bigskip
\end{center}
\end{minipage}
}

\newpage
\begin{tabular}{|c|c|c|c|c|c|}\hline
 & a & i & u & e & o \\\hline
-&\Kletter{a}&\Kletter{i}&\Kletter{u}&\Kletter{e}&\Kletter{o}\\\hline
\end{tabular}

% ===========================================================================
\chapter{専門用語 - Terminology}

\input{../share/sec/Manyogana} % label sec:Manyogana

\input{../share/sec/Hepburn} % label sec:Hepburn

\input{../share/sec/Kunrei} % label sec:Kunrei

\input{../share/sec/Diphthong} % label: sec:Diphthong

\input{../share/sec/Mora} % label sec:Mora

\input{../share/sec/Syllable} % label sec:Syllable

\input{../share/sec/Dakuten} % label sec:Dakuten

\input{../share/sec/Handakuten} % label sec:Handakuten

\input{../share/sec/Iteration} % label sec:Iteration

\input{../share/sec/Radical} % label sec:Radical

% ===========================================================================
% END
% ===========================================================================
\end{document}
