%----------------------------------------------------------------------------
\section{Katakana \jtl{sa} Row}\jsec{片仮名サ行}\label{sec:KatakanaSaRow}

\Krow{sarow}{sa}{shi}{su}{se}{so}

\label{letter:sa}\KLETTER{sa} The  \textbf{katakana} \jquotesingleja{サ} is
pronounced \jtl{sa} and derives from the
\hyperref[sec:PhoneticCharacter]{phonetic character}s \jquotesingleja{散} upper
left corner \hyperref[sec:Radical]{radical}.  A \hyperref[sec:Dakuten]{dakuten}
version exists and pronounced as \jtl{za}.

\label{letter:shi}\KLETTER{shi} The \textbf{katakana} \jquotesingleja{シ}
derives from the \hyperref[sec:PhoneticCharacter]{phonetic character}　
\jquotesingleja{之 }.  It is pronounced as \jtl{shi}.  A
\hyperref[sec:Dakuten]{dakuten} version exists and pronounced as \jtl{ji}.

\Note{Note}{Please see section \nameref{subsec:ShiTsuAmbiguity} for the
explanation how to write and distinguish \jtl{shi} and \jtl{tsu}.  }

\label{letter:su}\KLETTER{su} The \textbf{katakana} \jquotesingleja{ス} derives
from the \hyperref[sec:PhoneticCharacter]{phonetic character}s right lower part
of \jquotesingleja{須}.  It is pronounced as \jtl{su}.  A
\hyperref[sec:Dakuten]{dakuten} version exists and pronounced as \jtl{zu}.

\label{letter:se}\KLETTER{se} The \textbf{katakana} \jquotesingleja{セ} derives
from the \hyperref[sec:PhoneticCharacter]{phonetic character}s middle left part
of \jquotesingleja{世}.  It is pronounced as \jtl{se}.  A
\hyperref[sec:Dakuten]{dakuten} version exists and pronounced as \jtl{ze}.

\newpage

\label{letter:so}\KLETTER{so} The \textbf{katakana} \jquotesingleja{ソ} derives
from the \hyperref[sec:PhoneticCharacter]{phonetic character}s upper right part
of \jquotesingleja{曽}.  It is pronounced as \jtl{so}.  A
\hyperref[sec:Dakuten]{dakuten} version exists and pronounced as \jtl{zo}.

\input{\jpsubsecl/SoRiNAmbiguity}

\newpage
% ---------------------------------------------------------------------------
\subsection{\jtl{sa}}\jsubsec{\jquotesingleja{サ}}\label{sec:KatakanaSa}

\KatakanaHeader{sa}{ Katakana \jquotesingleja{サ} is written with three
strokes. All crossings of strokes are in a 90 degree angle.  The starts of all
strokes are aligned either horizontally or vertically. The last stroke has a
curve.} \KatakanaTraining{sa}

% ---------------------------------------------------------------------------
\subsection{\jtl{shi}}\jsubsec{\jquotesingleja{シ}}\label{sec:KatakanaShi}

\KatakanaHeader{shi}{ The Katakana \jquotesingleja{シ} is written with three
strokes. All three strokes are aligned vertically in the beginning. Please see
section \nameref{subsec:ShiTsuAmbiguity}.} \KatakanaTraining{shi}

% ---------------------------------------------------------------------------
\subsection{\jtl{su}}\jsubsec{\jquotesingleja{ス}}\label{sec:KatakanaSu}

\KatakanaHeader{su}{The Katakana \jquotesingleja{ス} is written with two
strokes. The first stroke starts horizontally aligned. The second stroke
touches the first stroke at the beginning.} \KatakanaTraining{su}

% ---------------------------------------------------------------------------
\subsection{\jtl{se}}\jsubsec{\jquotesingleja{セ}}\label{sec:KatakanaSe}

\KatakanaHeader{se}{ The Katakana \jquotesingleja{セ} is written with two
strokes. The crossing has \textbf{no} 90 degree angle. The curve of the second
stroke as almost a 90 degree angle. } \KatakanaTraining{se}

% ---------------------------------------------------------------------------
\subsection{\jtl{so}}\jsubsec{\jquotesingleja{ソ}}\label{sec:KatakanaSo}

\KatakanaHeader{so}{ The Katakana \jquotesingleja{ソ} is written with two
strokes. The first stroke is not aligned vertically but it is aligned
horizontally withe the second stroke. Please see section
\nameref{subsec:SoRiNAmbiguity}.} \KatakanaTraining{so}

% ---------------------------------------------------------------------------
\subsection{\jtl{sa} Row Training}\jsubsec{片仮名サ行練習}\label{sec:SaRowTraining}
% 3 78 エキス
%3 357 スカイ
%3 360 スキー
%3 3 アイス
%3 111 ガーゼ
%3 146 イエス
\Padding
\begin{longtable}[c]{p{2cm}p{2cm}p{3cm}p{6cm}p{2cm}}
\textit{Katakana}&\textit{Rōmaji}&\textit{Original}&\textit{Remark}&\textit{Origin}\\\hline
エキス&ekisu&ex(tract)&extract&Dutch\\
スカイ&sukai&sky&&English\\
スキー&sukī&ski&noun for skiing&English\\
\end{longtable}
\KanaSimpleTraining{Katakana to Rōmaji}{
\Transcribe{1.}{エキス}{}{extract}      % ekisu
\Transcribe{2.}{スカイ}{}{sky}          % sukai
\Transcribe{3.}{スキー}{}{ski}          % sukī
\Transcribe{4.}{アイス}{}{ice}          % aisu
\Transcribe{5.}{ガーゼ}{}{gauze}        % gāze
%\Transcribe{6.}{イエス}{}{Jesus}        % iesu
}

\KanaSimpleTraining{Rōmaji to Katakana}{
\Transcribe{1.}{sukai}{}{sky}         % sukai
\Transcribe{2.}{ekisu}{}{extract}     % ekisu
\Transcribe{3.}{aisu}{}{ice}          % aisu
\Transcribe{4.}{suki}{}{ski}          % sukī
\Transcribe{5.}{iesu}{}{Jesus}        % iesu
%\Transcribe{6.}{gāze}{}{gauze}        % gāze
}

\newpage

\Padding
\begin{longtable}[c]{p{2cm}p{2cm}p{3cm}p{6cm}p{2cm}}
\textit{Katakana}&\textit{Rōmaji}&\textit{Original}&\textit{Remark}&Origin\\\hline
アイス&aisu&ice&water ice, ice cream&English\\
ガーゼ&gāze&Gaze&gauze&German\\
イエス&iesu&Jesus&Jesus&Portuguese\\
\end{longtable}
\KanaSimpleTraining{English to Rōmaji}{
\Transcribe{1.}{extract}{}{}       % ekisu
\Transcribe{2.}{sky}{}{}           % sukai
\Transcribe{3.}{Jesus}{}{}         % iesu
\Transcribe{4.}{gauze}{}{}         % gāze
\Transcribe{5.}{ice}{}{}           % aisu
%\Transcribe{6.}{ski}{}{}           % sukī
}

\KanaSimpleTraining{English to Katakana}{
\Transcribe{1.}{sky}{}{}           % sukai
\Transcribe{2.}{gauze}{}{}         % gāze
\Transcribe{3.}{ice}{}{}           % aisu
\Transcribe{4.}{Jesus}{}{}         % iesu
\Transcribe{5.}{extract}{}{}       % ekisu
%\Transcribe{6.}{ski}{}{}           % sukī
}

\newpage
