% ---------------------------------------------------------------------------
\section{Katakana \jtl{ta} Row}\jsec{片仮名タ行}\label{sec:KatakanaTaRow}

\Krow{tarow}{ta}{chi}{tsu}{te}{to}

\label{letter:ta}\KLETTER{ta} The  \textbf{katakana} \jquotesingleja{タ} is
pronounced \jtl{ta} and derives from the
\hyperref[sec:PhoneticCharacter]{phonetic character}s \jquotesingleja{多 }
upper or lover \hyperref[sec:Radical]{radical}.  A
\hyperref[sec:Dakuten]{dakuten} version exists and pronounced as \jtl{da}.

\label{letter:chi}\KLETTER{chi} The \textbf{katakana} \jquotesingleja{チ}
derives from the \hyperref[sec:PhoneticCharacter]{phonetic character}　
\jquotesingleja{千}.  It is pronounced as \jtl{chi}.  A
\hyperref[sec:Dakuten]{dakuten} version exists and pronounced as \jtl{ji}.

\label{letter:tsu}\KLETTER{tsu} The \textbf{katakana} \jquotesingleja{ツ}
derives from the \hyperref[sec:PhoneticCharacter]{phonetic character}s
\jquotesingleja{州} or \jquotesingleja{川} .  It is pronounced as \jtl{tsu}.  A
\hyperref[sec:Dakuten]{dakuten} version exists and pronounced as \jtl{zu}.

\label{letter:te}\KLETTER{te} The \textbf{katakana} \jquotesingleja{テ} derives
from the \hyperref[sec:PhoneticCharacter]{phonetic character}s lower left part
of \jquotesingleja{天 }.  It is pronounced as \jtl{te}.  A
\hyperref[sec:Dakuten]{dakuten} version exists and pronounced as \jtl{de}.

\newpage

\label{letter:to}\KLETTER{to} The \textbf{katakana} \jquotesingleja{ト} derives
from the \hyperref[sec:PhoneticCharacter]{phonetic character}s right part of
\jquotesingleja{止}.  It is pronounced as \jtl{to}.  A
\hyperref[sec:Dakuten]{dakuten} version exists and pronounced as \jtl{do}.

\input{\jpsubsecl/ShiTsuAmbiguity}

\newpage

% ---------------------------------------------------------------------------
\subsection{\jtl{ta}}\jsubsec{\jquotesingleja{タ}}\label{sec:KatakanaTa}

\KatakanaHeader{ta}{ Katakana \jtl{ta} is written with three strokes. The first
stroke is a small curve. The secosnd stroke starts horizontally attached to the
first stroke. The third stroke ends at the second stroke.}
\KatakanaTraining{ta}

% ---------------------------------------------------------------------------
\subsection{\jtl{chi}}\jsubsec{\jquotesingleja{チ}}\label{sec:KatakanaChi}

\KatakanaHeader{chi}{ Katakana \jtl{chi} is written with three strokes. The
first stroke is a light curve. The second ihorizontally straight line. The
third line is a curve that joints the first and the second.}
\KatakanaTraining{chi}

% ---------------------------------------------------------------------------
\subsection{\jtl{tsu}}\jsubsec{\jquotesingleja{ツ}}\label{sec:KatakanaTsu}

\KatakanaHeader{tsu}{Katakana \jtl{tsu} is written with three strokes. The
first and second stroke are short. And the beginning of all three strokes is
aligned horizontally. The third stroke is the longest, but the end is not
alignd wit the beginning of the first stroke. } \KatakanaTraining{tsu}

% ---------------------------------------------------------------------------
\subsection{\jtl{te}}\jsubsec{\jquotesingleja{テ}}\label{sec:KatakanaTe}

\KatakanaHeader{te}{ Katakana \jtl{te} is written with three strokes. The first
stroke is the shortest and horizontally. The second stroke is not aligned
vertically in the beginning, but also perfectly horizontally. The third stroke
is a small curve attached to the middle of the second stroke. }
\KatakanaTraining{te}

% ---------------------------------------------------------------------------
\subsection{\jtl{to}}\jsubsec{\jquotesingleja{ト}}\label{sec:KatakanaTo}

\KatakanaHeader{to}{ Katakana \jtl{to} is written with 2 strokes. The first
stroke is a vertical line. Attached to this line there is short straight line
to the right. In some hand writings this line is a small curve to the right.}
\KatakanaTraining{to}

% ---------------------------------------------------------------------------
\subsection{\jtl{ta} Row Training}\jsubsec{片仮名タ行練習}
\Padding
\begin{longtable}[c]{p{2cm}p{2cm}p{3cm}p{6cm}p{2cm}}
\textit{Katakana}&\textit{Rōmaji}&\textit{Original}&\textit{Remark}&\textit{Origin}\\\hline
エステ        &esutei    &esthé(tique)&beauty salon, esthetic clinic    &French\\
サイト        &saito     &site        &&English\\
タスク        &tasuku    &task        &&English\\
\end{longtable}

\KanaSimpleTraining{Katakana to Rōmaji}{
\Transcribe{1.}{エステ}{}{esthé(tique)}
\Transcribe{2.}{サイト}{}{site}
\Transcribe{3.}{タスク}{}{task}
\Transcribe{4.}{テスト}{}{test}
\Transcribe{5.}{スーツアクター}{}{suit actor}
%\Transcribe{6.}{テキスト}{}{text}
}

\KanaSimpleTraining{Rōmaji to Katakana}{
\Transcribe{1.}{saito}{}{site}
\Transcribe{2.}{tasuku}{}{task}
\Transcribe{3.}{esute}{}{esthé(tique)}
\Transcribe{4.}{sūtsuakutā}{}{suit actor}
\Transcribe{5.}{tesuto}{}{test}
%\Transcribe{6.}{テキスト}{}{text}
}

\newpage
\Padding
\begin{longtable}[c]{p{2.6cm}p{2cm}p{1.8cm}p{6.6cm}p{1.8cm}}
\textit{Katakana}&\textit{Rōmaji}&\textit{Original}&\textit{Remark}&\textit{Origin}\\\hline
テスト        &tesuto    &test        &                                 &English\\
スーツアクター&sūtsuakutā&suit actor  &wearing cartoon-character costume&English\\
テキスト      &tekisuto  &text        &                                 &English\\
\end{longtable}

\KanaSimpleTraining{English to Rōmaji}{
\Transcribe{1.}{task}{}{}
\Transcribe{2.}{esthé(tique)}{}{}
\Transcribe{3.}{text}{}{}
\Transcribe{4.}{test}{}{}
\Transcribe{5.}{suit actor}{}{}
%\Transcribe{6.}{site}{}{}
}

\KanaSimpleTraining{English to Katakana}{
\Transcribe{2.}{esthé(tique)}{}{}
\Transcribe{4.}{test}{}{}
\Transcribe{5.}{suit actor}{}{}
\Transcribe{3.}{text}{}{}
\Transcribe{6.}{site}{}{}
%\Transcribe{1.}{task}{}{}
}

\newpage
