\chapter*{Introduction}\jchap{前書き}
\addcontentsline{toc}{chapter}{Introduction}
% FOREWORD:     Vorwort        (someone else: why you should read?)
% INTRODUCTION: Einfuehrung    (author: what is in it, what can be expected?)
% PREFACE:      Vorbemerkungen (author: why the book exists?)
% [o] LABEL
\label{chap:Introduction}
% [o] INDEX DESTINATION (DEF) \ifor only
% [o] INDEX TARGET
\ithree{introduction}{前書き}{Einleitung}
\ifor{hiragana}{平仮名}{ひらがな}{Hiragana}
\ifor{katakana}{片仮名}{かたかな}{Katakana}

\textbf{The Japanese Language - Nihongo} series has two volumes with the aim to
teach the two Japanese syllable scripts: Volume \jvolumes{①} \textbf{hiragana}
and volume \jvolumes{②} \textbf{katakana}.%
%
\jhiraganaonly{

This book is the \textbf{first} volume \jvolumes{①} of \textit{The Japanese
Language - Nihongo series} that can be used to learn the Japanese script called
\textbf{hiragana}.

}
%
\jkatakanaonly{

This book is the \textbf{second} volume \jvolumes{②} of \textit{The Japanese
Language - Nihongo} series that can be used to learn the Japanese script called
\textbf{katakana}.

}

While there is no specific reason to start with \jtopic or \jtopicopposite when
it comes to learn the first Japanese writing script, historically
\textbf{hiragana} is the first choice. It might be the assumption that hiragana
are more common in Japanese texts than katakana and also when Japanese Chinese
characters (kanji) are transcribed (for example as station names) hiragana is
used. However, since a beginner in learning Japanese also have almost no
vocabulary knowledge, the usability is overestimated by native Japanese people.
Actually, a foreigner from an English speaking background might consider to
learn katakana first, because foreign words in Japanese are written in katakana
and after mastering katakana such learner would be able to read and write
thousands of words with a little imagination, compared to almost none in case
of hiragana. \jhiraganaonly{This book assumes that you learn \textbf{hiragana}
either as first or second script.} \jkatakanaonly{This book assumes that you
learn \textbf{katakana} as first or second script.}

With whatever script to start with, it is recommended to finish the first
script and only then learn the second script. It is also recommended to finish
hiragana \textbf{and} katakana before learning Japanese Chinese characters
(kanji).

Common chapters are repeated or are slightly modified in each volume, so that a
learner can choose to start with volume {\jvolumes{①}} or {\jvolumes{②}} and
obtain all the references in each volume. Skip the passages you already know.

\input{\jpsecl/SelfLearning}

\input{\jpsecl/Usage}
