% +---------------------------------------------------------------------------+
% | english/chap/TheWayToWrite.tex                                            |
% |                                                                           |
% | Katakana or hiragana specific information                                 |
% |                                                                           |
% | Version: 0.1.1                                                            |
% |                                                                           |
% | Changes:                                                                  |
% |                                                                           |
% | 0.1.1 2023-06-05 Christian Külker <c@c8i.org>                             |
% |     - Improve English writing                                             |
% | 0.1.0 2022-09-10 Christian Külker <c@c8i.org>                             |
% |     - Initial version (disable input KanaPronunciation)                   |
% |                                                                           |
% +---------------------------------------------------------------------------+

\ifthenelse{\equal{hiragana}{\jtopic}}{%
\chapter{The Way to Write Hiragana}\jchap{平仮名の書き方}
% [o] LABEL
\label{chap:TheWayToWriteHiragana}
% [o] DESTINATIONS
% [o] INDEX
\ien{The Way to Write Hiragana}
\ien{hiragana!writing}
\ide{Hiragana!schreiben}
}{}%
\ifthenelse{\equal{katakana}{\jtopic}}{%
\chapter{The Way to Write Katakana}\jchap{片仮名の書き方}
% [o] LABEL
\label{chap:TheWayToWriteKatakana}
% [o] DESTINATIONS
% [o] INDEX
\ien{The Way to Write Katakana}
\ien{katakana!writing}
\ide{Katakana!schreiben}
}{}%
% [o] DESTINATIONS
\ifor{gojūonzu}{五十音図}{ごじゅうおんず}{50@50 Laute Tafel}
\ifor{mora}{モーラ}{もーら}{Mora}
\ifor{space character}{空白文字}{くうはく･もじ}{Leerzeichen}
\ifor{kanji}{漢字}{かんじ}{Kanji}

This chapter explains how to read and write \jkanavoc. After introducing the
sound structure, the traditional way of displaying and ordering \jtopic{} is
presented. A short section lists the functions of \jtopic, what \jtopic{} is
used for. The following section briefly introduces the pronunciation. Since
this book focuses on writing, the majority of the sections teach how to write
\jtopic{} and inform about special \jtopic{} as well as general punctuation.
The last part is about rarely used \jtopic.

\jscript{} derived from \textbf{Chinese} characters, called
\hyperref[sec:Kanji]{kanji}. All \jtopic{} together form a complete phonetic
script with less than 50 characters (or morae). This script can be used to
write all Japanese words.

\ifor{gojūonzu}{五十音図}{ごじゅうおんず}{50@50 Laute Tafel}

The \textbf{\jtopic} collection is usually displayed in the
\hyperref[sec:Gojuonzu]{gojūonzu} (lit. table of fifty sounds), a grid of 10x5
fields in which the characters are displayed. Although the
\hyperref[sec:Gojuonzu]{gojūonzu} nominally contains 50 characters, the grid is
not completely filled. There is also an extra character at the end. So with
five columns and one extra character, the current number of \textbf{\jtopic} is
47. %
\ifthenelse{\equal{hiragana}{\jtopic}}{
The script has no character for doubling a vowel (which would not be displayed
in the \hyperref[sec:Gojuonzu]{gojūonzu} anyway). Unlike \textbf{katakaka} with
47, \textbf{hiragana} has 46 different characters, still under 50.
}{}%
\ifthenelse{\equal{katakana}{\jtopic}}{
If we count the character for doubling a vowel (which is unfortunately not
shown in the \hyperref[sec:Gojuonzu]{gojūonzu}). Unlike \textbf{hiragana} with
46, \textbf{katakana} has 47 different characters, still under 50.
}{}%

\input{\jptab/Gojuonzu}

This document is structured according to the \hyperref[sec:Gojuonzu]{gojūonzu},
five \textbf{\jtopic} are introduced in one section to be learned together.

\ifor{space character}{空白文字}{くうはく･もじ}{Leerzeichen}
\ifor{homophone}{同音異語}{どうおん･いご}{Homophon}
\ija{同音語}

Although \textbf{\jtopic} can be used by itself to express the complete content
of the Japanese language, it is rarely used as such. The use of all Japanese
scripts \textbf{hiragana}, \textbf{katakana} and \hyperref[sec:Kanji]{kanji}
has the advantage that word boundaries can be easily seen and the
\hyperref[sec:SpaceCharacter]{space character} is unnecessary. So a Japanese
\textbf{\jtopic} sentence with only \textbf{\jtopic} and no
\hyperref[sec:SpaceCharacter]{space character} is hard to understand because it
is impossible to distinguish words. However, even if
\hyperref[sec:SpaceCharacter]{space character} were introduced as in Roman
languages, Japanese has so many \hyperref[sec:Homophone]{homophones} that it
would still be very difficult to impossible to understand sentences.
Especially \hyperref[sec:Kanji]{kanji} give context and meaning. Therefore, the
boundaries of script types (\hyperref[sec:Hiragana]{hiragana},
\hyperref[sec:Katakana]{katakana}, and \hyperref[sec:Kanji]{kanji}) are the
most important indicators of word boundaries.

\ifor{hiragana}{平仮名}{ひらがな}{Hiragana}
\ifor{katakana}{片仮名}{かたかな}{Katakana}
\ifor{okurigana}{送り仮名}{おくりがな}{Okurigana}
\ien{role}\ija{機能}\ija{きのう}\ide{Funktion}
\ide{Rolle}

\phantomsection
\label{sec:role}

In the Japanese written language, each character has a role. The role of
\textbf{\jtopic} has changed over time. The last big change was after the end
of World War II and \textbf{\jtopic} got the roles it still has today and they
are fixed for the time being.

\bigskip

\input{\jptabl/Function}

\medskip

\ifor{manga}{漫画}{まんが}{Manga}

Therefore, in commercials, \hyperref[sec:Manga]{manga} and literature
describing foreign concepts, \textbf{katakana} has a over proportionate use.

%\input{\jpsecl/KanaPronunciation}
\input{\jpsecl/WritingLetters}
%\input{../share/sec/WritingKatakanaSentences}
\input{\jpsecl/SpecialKanaCharacters}

