% ===========================================================================
\chapter{The Way to Write Katakana}\jchap{片仮名の書き方}
% [o] LABEL
\label{chap:TheWayToWriteKatakana}
% [o] DESTINATIONS
% [o] INDEX
\ifor{Gojūonzu}{五十音図}{ごじゅうおんず}{50@50 Laute Tafel}
\ifor{mora}{モーラ}{もーら}{Mora}
\ifor{space character}{空白文字}{くうはく･もじ}{Leerzeichen}
\ien{The Way to Write Katakana}
\ien{Katakana!writing}
\ide{Katakana!schreiben}
\ifor{Kanji}{漢字}{かんじ}{Kanji}

The second\footnote{The first is \hyperref[sec:Hiragana]{Hiragana}} Japanese
\hyperref[sec:Kana]{Kana} script a -- \hyperref[sec:Mora]{mora} based writing
system -- is called \textbf{Katakana} and this is written in Japanese as
{片仮名} {【かたかな】} but sometimes also as {カタカナ} {【かたかな】}. It
consists of a little less then 50 letters, as it is usual for
\hyperref[sec:Mora]{morae} or \hyperref[sec:Syllable]{syllable} based systems.
\textbf{Katakana} derived from Chinese characters, called
\hyperref[sec:Kanji]{Kanji} ( {漢字}　{【かんじ】} in Japanese). All
\textbf{Katakana} together form a complete phonetic script.

\ifor{Gojūonzu}{五十音図}{ごじゅうおんず}{50@50 Laute Tafel}

The collection of \textbf{Katakana} is usually displayed in the
\hyperref[sec:Gojuonzu]{Gojūonzu} (lit. Table of Fifty Sounds), a grid of 10x5
in which the characters are displayed. Even though nominally the
\hyperref[sec:Gojuonzu]{Gojūonzu} is containing 50 characters the grid is not
completely occupied. Additionally there is also one character added to the end.
So with five columns and one extra letter, the current number of
\textbf{Katakana} is 46. If we would count also the character for doubling a
vowel (which is not displayed in the \hyperref[sec:Gojuonzu]{Gojūonzu}) we have
47 distinct characters, still below 50.

\input{../share/table/GuonjizuKatakana}

This document is structured according to the \hyperref[sec:Gojuonzu]{Gojūonzu},
five \textbf{Katakana} will be introduced in one section to be learned
together.


\ifor{space character}{空白文字}{くうはく･もじ}{Leerzeichen}
\ifor{homophone}{同音異語}{どうおん･いご}{Homophon}
\ija{同音語}

Even though \textbf{Katakana} can be used by its own to express the complete
content of the Japanese language it is almost never used as such. This is due
to the fact that the other two scripts \hyperref[sec:Hiragana]{Hiragana} and
\hyperref[sec:Kanji]{Kanji} exist and that there was traditionally no
\hyperref[sec:SpaceCharacter]{space character} to separate words. So a
\textbf{Katakana} sentence with \textbf{Katakana} only and no
\hyperref[sec:SpaceCharacter]{spaces} is hardly understandable also due to many
\hyperref[sec:Homophone]{homophones}. But even if there are
\hyperref[sec:SpaceCharacter]{spaces} it is difficult. Therefore the letter
type boundaries of \hyperref[sec:Kanji]{Kanji},
\hyperref[sec:Hiragana]{Hiragana} and \textbf{Katakana} are the most
significant indicator for word boundaries.

\ifor{Hiragana}{平仮名}{ひらがな}{Hiragana}
\ifor{Okurigana}{送り仮名}{おくりがな}{Okurigana}
\ien{role}\ija{機能}\ija{きのう}\ide{Funktion}
\ide{Rolle}
\ifor{Katakana}{片仮名}{かたかな}{Katakana}

\phantomsection
\label{sec:role}

In the Japanese\footnote{Until the end of World War II \textbf{Katakana} was
used differently. Official documents used a mix of \hyperref[sec:Kanji]{Kanji}
and \textbf{Katakana} in a similar way then \hyperref[sec:Hiragana]{Hiragana}
and \hyperref[sec:Kanji]{Kanji} today. \textbf{Katakana} was used for
Particles and \hyperref[sec:Okurigana]{Okurigana}.} written language
\textbf{Katakana} has a distinct role. It serves for:

\bigskip

\ifor{manga}{漫画}{まんが}{Manga}

\begin{tabular}{rp{15cm}}
1.& writing words of foreign origin\\
2.& words that need to be emphasized\\
3. &often indicate on-yomi in dictionaries\\
4.& names of minerals \\
5.& geological names \\
6.& names of fauna (animals)\\
7.& names of flora (plants)\\
8.& partly onomatopoeias in \hyperref[sec:Manga]{manga}\\
9.& sounds, like animal sounds or sounds made by humans\\
10.& telegrams (before 1988)\\
11.& banking system account names\\
12.& In literature (eg. \hyperref[sec:Manga]{manga}) words being spoken in a
(foreign) accent or "robotic" speech\\
13. &sometimes used as Furigana\\
14. & uncommon \hyperref[sec:Kanji]{Kanji}, eg. {皮膚科} {【ひふか】}
"dermatologist" written as {皮フ科}\\
15.& computer output (in 80s, before introduction of multi byte characters)\\
16. &some personal names (especially female) (common in the past: eg.
セツ (setsu))\\

\end{tabular}

\medskip

\ifor{manga}{漫画}{まんが}{Manga}

Therefore in commercials, \hyperref[sec:Manga]{manga} and literature describing
foreign concepts \textbf{Katakana} has a over proportional usage.

\input{../share/sec/KatakanaPronunciation}
\input{../share/sec/WritingKatakanaLetters}
%\input{../share/sec/WritingKatakanaSentences}
\input{../share/sec/SpecialKatakanaCharacters}
