\chapter{Writing Katakana - 片仮名の書き方}

The second\footnote{The first is Hiragana} Japanese Kana script a
\hyperref[sec:Mora]{mora}  based writing system is called Katakana and this is
written in Japanese as {片仮名} {【かたかな】} but sometimes also as
{カタカナ}.  It consists of a little less the 50 letters, as it is usual for
morae or \hyperref[sec:Syllable]{syllable} based systems. Katakana derived from
Chinese characters, called Kanji ( {漢字}　{【かんじ】} in Japanese). All
Katakana together form a complete phonetic script.

The collection of Katakana is usually displayed in the Gojūonzu (lit. Table of
Fifty Sounds), a grid of 10x5 in which the characters are displayed. Even
though nominally the Gojūonzu is containing 50 characters the grid is not
completely occupied. Additionally there is also one character added to the
end. So with five gabs and one extra letter, the current number of Katakana is
46. If we would count also the character for doubling a vowel (which is not
displayed in the Gojūonzu) we have 47 distinct characters, still below 50. 

\input{../share/table/GuonjizuKatakana}

Even though Katakana can be used by its own to express the complete content of
the Japanese language it is almost never used as such. This is due to the fact
that the other two scripts Hiragana and Kanji exists and that there was
traditionally no space character to separate words. So a Katakana sentence with
Katakana only and no spaces is hardly understandable also due to many
homophones.  But even if there are spaced it is difficult. Therefore the letter
type boundaries of Kanji, Hirangana and Katakana are the most significant
indicator for word boundaries.

In the Japanese\footnote{Until the end of World War II Katakana was used
differently. Official documents used a mix of Kanji and Katakana in a similar
way then Hiragana and Kanji today. Katakana was used for Particles and
Okurigana.} written language Katakana has a distinct role. It serves for:

\bigskip

\begin{tabular}{rp{15cm}}
1.& writing words of foreign origin\\
2.& words that need to be emphasized\\
3. &often indicate on-yomi in dictionaries\\
4.& names of minerals \\
5.& geological names \\
6.& names of fauna (animals)\\
7.& names of flora (plants)\\
8.& partly onomatopoeias in Manga\\
9.& sounds, like animal sounds or sounds made by humans\\
10.& Telegrams (before 1988)\\
11.& banking system account names\\
12.& In literature (eg. Manga) words being spoken in a (foreign) accent or "robotic" speech\\
13. &sometimes used as Furigana\\
14. & uncommon Kanji, eg.  {皮膚科} {【ひふか】} "dermatologist" written as {皮フ科}\\
15.& computer output (in 80th, before introduction of multi byte characters)\\
16. &some personal names (especially female) (common in the past: eg. セツ (setsu))\\
\end{tabular}

\medskip

Therefore in commercials, Manga and literature describing foreign concepts
Katakana has a over proportional usage.

\input{../share/sec/KatakanaPronunciation}
\input{../share/sec/WritingKatakanaLetters}
%\input{../share/sec/WritingKatakanaSentences}
\input{../share/sec/SpecialKatakanaCharacters}
