1300 years ago the first endeavours where undertaken to display the Japanese
language with the only known alphabet in the region, the Chinese writing
system. While the Japanese language where hardly suited for the writing system
it was an  economical choice since the Chinese characters where well developed
at that time and introduced many new ideas in lexis. The 'borrowing' of Chinese
characters was not a one shot operation it took centuries and more then one
attempt. This long winded process led to the fact that some characters where
imported more then once from China from different times and different regions.
And because of this one Chinese character can have more then one pronunciation.
We hope that this will consolidate over the next centuries.  Today this
imported characters are known as \textbf{Kanji} in Japan.  \textbf{Kanji} is
written \textit{Hanzi} in Chinese and referencing the character from the Han
period of China. Even though today all Chinese based characters (and even some
self invented) are referenced nowadays as \textbf{Kanji}, it does not strictly
mean that they only from the Han period.

A standard Japanese text do contain \textbf{Kanji}. To master the Japanese
language over a certain level and to be over come the problem of personal
illiteracy in Japan it is highly encouraged to learn at least 600 to 800
characters. To become fully literate member of the Japanese society 2000 to
2300 \textbf{Kanji} should be learned.

Today  \textbf{Kanji} in written Japanese language are used for substantives/
nouns, verbs, adjectives and names.
