% +---------------------------------------------------------------------------+
% | SpecialKanaCharacters.tex                                                 |
% |                                                                           |
% | Collect special hiragana and katakana characters                          |
% |                                                                           |
% | Version: 0.1.3                                                            |
% |                                                                           |
% | Changes:                                                                  |
% |                                                                           |
% | 0.1.3 2024-04-02 Christian Külker <c@c8i.org>                             |
% |     - Improve clarity and grammar for katakana                            |
% | 0.1.2 2024-04-02 Christian Külker <c@c8i.org>                             |
% |     - Fix doubling hiragana (oo vs. ou)                                   |
% | 0.1.1 2024-03-29 Christian Külker <c@c8i.org>                             |
% |     - Fix typos                                                           |
% | 0.1.0 2022-08-02 Christian Külker <c@c8i.org>                             |
% |     - Merge katakana and hiragana                                         |
% |                                                                           |
% +---------------------------------------------------------------------------+

\ifthenelse{\equal{hiragana}{\jtopic}}{%
\section{Special Hiragana Characters}\jsec{特別ひらがな}
% LABEL
\label{sec:SpecialHiraganaCharacters}
\label{sec:SpecialKanaCharacters}
% INDEX
\ifor{special hiragana characters}{特別ひらがな}{とくべつひらがな}{Spezielle Hiragana Zeichen}
}{}
\ifthenelse{\equal{katakana}{\jtopic}}{%
\section{Special Katakana Characters}\jsec{特別カタカナ}
% LABEL
\label{sec:SpecialKatakanaCharacters}
\label{sec:SpecialKanaCharacters}
% INDEX
\ifor{special katakana characters}{特別カタカナ}{とくべつかたかな}{Spezielle Katakana Zeichen}
}{}
% INDEX
\ifor{hiragana}{平仮名}{ひらがな}{Hiragana}
\ifor{gojūonzu}{五十音図}{ごじゅうおんず}{50@50 Laute Tafel}

As mentioned previously, both \textbf{kana} syllables are almost identical,
except for their shapes. This is particularly evident in the
\hyperref[sec:Gojuonzu]{gojūonzu (50 sound table)}. This section will highlight
the special characters, some of which differ from the standard \jtopic{} set.

%TODO check if point changes orientation and alignment in case of changing
%writing direction.

\ifthenelse{\equal{hiragana}{\jtopic}}{%
\subsection{Doubling Vowels in Hiragana}\jsubsec{ひらがなでの倍増母音}
}{}
\ifthenelse{\equal{katakana}{\jtopic}}{%
\subsection{Doubling Vowels in Katakana}\jsubsec{カタカナでの倍増母音}
}{}
% [o] LABEL
\label{subsec:DoublingVowelsIn\jscript}
\label{subsec:DoublingVowels}
\label{sec:DoublingVowelsIn\jscript}
\label{sec:DoublingVowels}
% [o] INDEX
\ifor{doubling vowels}{倍増母音}{ばいぞうぼいん}{Vokalverdopplung}
\ifor{repetition mark}{繰り返し記号}{くりかえしきごう}{Wiederholungszeichen}
\ifor{hiragana}{平仮名}{ひらがな}{Hiragana}
\ifor{katakana}{片仮名}{かたかな}{Katakana}

% ひらがなでの倍増母音 【ばいぞうぼいん】
% カタカナでの倍増母音 【ばいぞうぼいん】

\ifthenelse{\equal{hiragana}{\jtopic}}{%

The usual way to double a vowel in \textbf{hiragana} is to write that hiragana
again. In the hiragana \jquotesingleja{お} character can be doubled with either
\jquotesingleja{う} or \jquotesingleja{お} . So \jtl{ō} becomes either
\jquotesingleja{おう} or \jquotesingleja{おお}. There is no rule to it. This
has to be rememberd. However in most cases \jquotesingleja{お} is doubled as
\jquotesingleja{おう}.

}{}
\ifthenelse{\equal{katakana}{\jtopic}}{%

Special \hyperref[sec:Katakana]{katakana} characters also exist. The most
important is \ivoc{chōon}{長音}{ちょうおん}{Chōon}, the plain iteration
character \jquotesingleja{ー}, represented as a stroke. It is one of the few
characters that change orientation according to the writing direction. When
writing katakana horizontally (left to right), the iteration character is
horizontal; when writing vertically (top to bottom), it is vertical. This
character's function is to double the duration of the preceding mora, which is
different from \hyperref[sec:Hiragana]{hiragana}. (For more on doubling using
other katakana characters, refer to section \nameref{sec:Iteration} on page
\pageref{sec:Iteration}.)

\bigskip

\CharacterExplanation{k-iteration-s}{In standard gothic fonts, the
\hyperref[sec:Katakana]{katakana} iteration character appears as a simple
straight line, making it ambiguous in terms of writing direction.}

\bigskip

\CharacterExplanation{k-iteration-sm}{However, when written in different fonts
or with a brush, it is apparent that the character should be written from left
to right in horizontal writing.}

}{}
\bigskip

%\definecolor{orange}{rgb}{1,0.5,0}
%\definecolor{mygreen}{rgb}{.2,1,.2}

\setCJKfamilyfont{cjk-horiz-m}[Script=CJK,RawFeature=horizontal]{IPAMincho}
\setCJKfamilyfont{cjk-horiz-g}[Script=CJK,RawFeature=horizontal]{IPAPGothic}
%\setCJKfamilyfont{cjk-vert}[Script=CJK,RawFeature=vertical]{Kozuka Gothic Pro M}
\setCJKfamilyfont{cjk-vert-m}[Script=CJK,RawFeature=vertical]{IPAMincho}
\setCJKfamilyfont{cjk-vert-g}[Script=CJK,RawFeature=vertical]{IPAPGothic}

\bigskip
\textit{Example:}

\bigskip

\begin{figure}[H]
\begin{center}
\begin{tabular}{p{7cm}p{7cm}}
Katakana:&Hiragana:\\
\CJKfamily{cjk-horiz-h}
\Huge カ\textbf{\color{magenta}ー}ド \jtl{kaado} &
\Huge か\textbf{\color{magenta}あ}ど \jtl{kaado}\\
\CJKfamily{cjk-horiz-g}
\Huge カ\textbf{\color{magenta}ー}ド \jtl{kaado} &
                                                \\
\end{tabular}
\end{center}
\caption{Kana vowel doubling example}
\label{fig:KanaVowlDoublingExample}
\end{figure}

\bigskip

This character is frequently used and makes \hyperref[sec:Katakana]{katakana}
easier to learn than hiragana. Unlike hiragana, it does not have long vowel
ambiguity.

As mentioned earlier, the orientation of the \hyperref[sec:Katakana]{katakana}
iteration mark changes with the direction of writing. The preceding example
demonstrates this with various writing orientations.

\medskip
\textit{Example:}

\medskip

\begin{figure}[H]
\begin{center}
\begin{tabular}{p{3.5cm}p{3.5cm}p{3.5cm}m{3.5cm}}
horizontally&
\mbox{
\begin{minipage}{3.2cm}
\CJKfamily{cjk-horiz-h}
\Huge カ\textbf{\color{magenta}ー}ド
\CJKfamily{cjk-horiz-g}
\Huge カ\textbf{\color{magenta}ー}ド
\end{minipage}
}
& vertically &
\raisebox{-.5\height}{
\mbox{
\rotatebox{-90}{
\begin{minipage}{3.2cm}
\CJKfamily{cjk-vert-m}
\Huge カ\textbf{\color{magenta}ー}ド
\CJKfamily{cjk-vert-g}
\Huge カ\textbf{\color{magenta}ー}ド
\end{minipage}
}
}
}
\\
\end{tabular}
\end{center}
\caption{Katakana horizontal and vertical vowel doubling example}
\label{fig:KatakanaHirzontalVerticalVowlDoublingExample}
\end{figure}

\medskip

% めったに使われない片仮名 【めったにつかわれないかたかな】
\ifthenelse{\equal{hiragana}{\jtopic}}{%
    \subsection{Seldom Used Hiragana}\jsubsec{めったに使われない平仮名}\label{subsec:SeldomlyUsedHiragana}

\ifor{voice!new writing}{声}{こえ}{Stimme!neue Schreibweise}
\ifor{voice!old writing}{声}{こゑ}{Stimme!alte Schreibweise}

All \textbf{hiragana} mentioned in the \hyperref[sec:Gojuonzu]{gojūonzu (50
sound table)} are used. There is no obsolete character in the table unlike the
\textbf{katakana} \jtl{wo} \jquotesingleja{ヲ}. However sometimes one can find
a \textbf{gojūonzu} with the additional characters: \jquotesingleja{ゐ} wi,
pronounced as \jtl{i}, and \jquotesingleja{ゑ} we, pronounced \jtl{e}, in the
\jtl{wa} row. This characters are old characters and normally not used. It is
safe to skip learning this characters. Words that used to have
\jquotesingleja{ゐ} had it replaced with \jquotesingleja{い} \jtl{i} and words
that used to have \jquotesingleja{ゑ} had it replaced with \jquotesingleja{え}
\jtl{e}. Examples: old \jquotesingleja{ゐる} is now written
\jquotesingleja{いる} \jtl{iru} ({居る} - to be somewhere), old
\jquotesingleja{こゑ} is now written as \jquotesingleja{こえ} \jtl{koe} ({声} -
voice).

}{}
% めったに使われない平仮名 【めったにつかわれないひらがな】
\ifthenelse{\equal{katakana}{\jtopic}}{%
    \subsection{Seldom Used Katakana}\jsubsec{めったに使われない片仮名}\label{subsec:SeldomlyUsedKatakana}

Because all particles are written in \textbf{hiragana} the particle
\textit{wo}, pronounced as \jtl{o}, is written with the hiragana
\jquotesingleja{を}. The \textbf{katakana} counterpart \textit{wo},
\jquotesingleja{ヲ}, also pronounced \jtl{o}, is included in the
\hyperref[sec:Gojuonzu]{gojūonzu}. However it is not used in modern texts and
it is not a particle in modern texts. It was used in old texts , such as
telegrams, as particle. Consequently, learners can typically omit the katakana
\jquotesingleja{ヲ} from their initial studies.

\label{sec:Wi}
\label{sec:We}
\ifor{we}{ヱ}{エ}{we}
\ifor{wi}{ヰ}{イ}{wi}

In some cases the \textbf{gojūonzu} contain archaic chrarcters:
\jquotesingleja{ヰ} wi, pronounced as \jtl{i}, and \jquotesingleja{ヱ} we,
pronounced \jtl{e}, in the \jtl{wa} row. These characters are old characters
and not used in contemporary Japanese. Therefore, it is generally unnecessary
for learners to focus on these characters. Historically, words containing
\jquotesingleja{ヰ} have had it replaced with \jquotesingleja{イ} (\jtl{i}),
and those with \jquotesingleja{ヱ} have transitioned to \jquotesingleja{エ}
(\jtl{e}).

}{}

